### 2025-08-04 paper/camera/sects/conclusion.tex
compact more

We also note that linear attention mechanisms, such as Performer~\cite{Choromanski20} and Mamba~\cite{Gu23}, could be leveraged to improve the scalability of \fname{} in environments with a large number of agents, without incurring the high computational cost associated with training classical Transformer architectures~\cite{Vaswani17}.

>>>>

Finally, linear attention mechanisms like Performer~\cite{Choromanski20} and Mamba~\cite{Gu23} could improve \fname{}'s scalability in large multi-agent environments while avoiding the computational overhead of classical Transformers~\cite{Vaswani17}.

### 2025-08-04 paper/camera/sects/discussion.tex
compact more

\subsection{Gradient Approximation with Neural Networks}
\begin{rqbox}
\textbf{Can we train a neural network to approximate the gradients of a differentiable simulator?}
\end{rqbox}

@@

\begin{replybox}
Yes, \fname{} approximates simulator gradients, achieving comparable performance to SHAC in differentiable settings, occasionally outperforming it despite initially higher variance.
\end{replybox}

\subsection{Comparison to PPO and SHAC}
\begin{rqbox}
\textbf{How does our algorithm compare to PPO and SHAC in both single-agent and multi-agent settings?}
\end{rqbox}

@@

\begin{replybox}
\fname{} outperforms PPO across all scenarios, with PPO struggling especially in multi-agent settings. When compared to SHAC (where applicable), \fname{} achieves comparable performance while enabling emergent cooperative behaviors.
\end{replybox}

\subsection{Scaling with Search Space}
\begin{rqbox}
\textbf{How does the performance of these algorithms change as the search space increases?}
\end{rqbox}

@@

\begin{replybox}
Performance varies with scale: Transport/Sampling converge faster with more agents, while Dispersion becomes harder. Cooperation emerges across scenarios. Main scalability limitation is transformer attention complexity, becoming prohibitive at large agent counts ($~$50), though moderate populations remain feasible.
\end{replybox}

>>>>

\subsection{Gradient Approximation with Neural Networks}
%\begin{rqbox}
\textbf{RQ:} \emph{Can we train a neural network to approximate the gradients of a differentiable simulator?}
%\end{rqbox}

@@

%\begin{replybox}
%Yes, \fname{} approximates simulator gradients, achieving comparable performance to SHAC in differentiable settings, occasionally outperforming it despite initially higher variance.
%\end{replybox}

\subsection{Comparison to PPO and SHAC}
%\begin{rqbox}
\textbf{RQ:} \emph{How does our algorithm compare to PPO and SHAC in both single-agent and multi-agent settings?}
%\end{rqbox}

@@

%\begin{replybox}
%\fname{} outperforms PPO across all scenarios, with PPO struggling especially in multi-agent settings. When compared to SHAC (where applicable), \fname{} achieves comparable performance while enabling emergent cooperative behaviors.
%\end{replybox}

\subsection{Scaling with Search Space}
%\begin{rqbox}
\textbf{RQ:} \emph{How does the performance of these algorithms change as the search space increases?}
%\end{rqbox}

@@

%\begin{replybox}
%Performance varies with scale: Transport/Sampling improve with more agents, while Dispersion degrades. Cooperation emerges consistently. Transformer attention limits scalability beyond ~50 agents.
%\end{replybox}

### 2025-08-04 paper/camera/sects/related.tex
compact more

\paragraph{Deep Reinforcement Learning}
Deep reinforcement learning has revolutionized policy learning tasks by combining reinforcement learning with deep neural networks.
Foundational works like DQN~\cite{Mnih13} (and its variants~\cite{Hessel18})
and AlphaZero~\cite{Silver17} demonstrated human-level performance in complex environments such as Atari games and chess.
Over the years, several algorithms have been proposed to create more stable and efficient learning methods.
Notable examples include A3C for asynchronous learning~\cite{Mnih16},
DDPG and PPO for continuous action spaces~\cite{DBLP:journals/corr/LillicrapHPHETS15,Schulman17} (also used in modern chatbot like ChatGPT),
and SAC for continuous action spaces with off-policy learning~\cite{DBLP:conf/icml/HaarnojaZAL18}.
Following the initial era of model-free algorithms,
model-based algorithms have been introduced to enhance sample efficiency.
Early works such as Dreamer~\cite{DBLP:conf/iclr/HafnerLB020} and PlaNet~\cite{DBLP:conf/icml/HafnerLFVHLD19} have demonstrated promising results in terms of both sample efficiency and performance.

\paragraph{Multi-Agent Reinforcement Learning}
Multi-Agent Reinforcement Learning (MARL) is a subfield of reinforcement learning that focuses on learning policies for multiple agents that interact with each other~\cite{albrecht2024multi}.
This field has a wide range of applications,
including robotics~\cite{DBLP:journals/air/ChungFYN24},
traffic control~\cite{DBLP:journals/tits/ChuWCL20},
and game playing~\cite{DBLP:conf/iclr/BakerKMWPMM20,jaderberg2019human},
and involves different types of agents such as cooperative, competitive, and mixed.
In this paper, we primarily focus on cooperative multi-agent scenarios,
where agents need to collaborate to achieve a common goal.
Prominent works in this area include extensions of single-agent algorithms to multi-agent settings,
such as MADDPG~\cite{DBLP:conf/nips/LoweWTHAM17} and MAPPO~\cite{DBLP:conf/nips/YuVVGWBW22},
as well as novel solutions to unique challenges in multi-agent settings. Examples of these solutions are COMA~\cite{DBLP:conf/aaai/FoersterFANW18} for multi-agent credit assignment,
QMIX~\cite{DBLP:conf/icml/RashidSWFFW18} for coordination in cooperative multi-agent settings,
and Mean Field MARL~\cite{Yang18} for handling a large number of agents.

>>>>

\paragraph{Deep Reinforcement Learning}
Reinforcement learning has achieved significant advancements through the integration of deep neural networks.
Foundational works such as DQN~\cite{Mnih13} and its variants~\cite{Hessel18}
and AlphaZero~\cite{Silver17} achieved human-level performance in complex environments.
Subsequent algorithms improved efficiency, including A3C~\cite{Mnih16}, 
DDPG and PPO for continuous control~\cite{DBLP:journals/corr/LillicrapHPHETS15,Schulman17}, 
and SAC for off-policy learning~\cite{DBLP:conf/icml/HaarnojaZAL18}.
Model-based approaches like Dreamer~\cite{DBLP:conf/iclr/HafnerLB020} and PlaNet~\cite{DBLP:conf/icml/HafnerLFVHLD19} 
later enhanced sample efficiency.

\paragraph{Multi-Agent Reinforcement Learning}
Multi-Agent Reinforcement Learning (MARL) is a subfield of reinforcement learning that focuses on learning policies for multiple agents that interact with each other~\cite{albrecht2024multi}.
This field has a wide range of applications,
including robotics~\cite{DBLP:journals/air/ChungFYN24},
traffic control~\cite{DBLP:journals/tits/ChuWCL20},
and game playing~\cite{DBLP:conf/iclr/BakerKMWPMM20},
and involves different types of agents such as cooperative, competitive, and mixed.
In this paper, we primarily focus on cooperative multi-agent scenarios where agents collaborate to achieve common goals.
Prominent works include extensions of single-agent algorithms like MADDPG~\cite{DBLP:conf/nips/LoweWTHAM17} and MAPPO~\cite{DBLP:conf/nips/YuVVGWBW22},
as well as novel solutions such as COMA~\cite{DBLP:conf/aaai/FoersterFANW18} for credit assignment,
QMIX~\cite{DBLP:conf/icml/RashidSWFFW18} for coordination,
and Mean Field MARL~\cite{Yang18} for large-scale scenarios.
